To log or not to log

### 2022-07-21 analysis/Analysis ECDC forecasts.Rmd
update manuscript

```{r}
# average number of cases and deaths
hub_data |>
  dplyr::select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value))

@@

ggsave("output/figures/HUB-mean-obs-location.png", width = 9, height = 5.5)

@@

```{r}

rankings <- scores |>
  select(-c(coverage_deviation, bias, ae_median, dispersion, underprediction, overprediction)) |>
  group_by(location, forecast_date, horizon, target_type, scale) |>
  mutate(ranking = rank(interval_score) / n()) |>
  ungroup()

rankings_diff <- rankings |>
  select(model, location, target_end_date, forecast_date, horizon,
         interval_score, scale, ranking, target_type) |>
  pivot_wider(names_from = scale, values_from = ranking, 
              id_cols = -interval_score)

plot_ranking_diffs <- function(
  rankings, 
  rankings_diff,
  target_type
) {
  type <- target_type
  # maybe replace this by the same ranking for all plots
  factor_levels <- rankings |>
    filter(horizon == 2, scale == "natural", target_type == type) |>
    group_by(model) |>
    summarise(ranking = mean(ranking)) |>
    arrange(-ranking) |>
    pull(model)

@@

  ranking_plot <- function(
    hor
  ) {
    p <- rankings_diff |>
      mutate(diff_ranking = natural - log) |>
      mutate(model = factor(model, levels = factor_levels)) |>
      filter(horizon == hor, 
             !is.na(model)) |>
      ggplot(aes(y = model, x = diff_ranking)) +
      geom_vline(linetype = "dashed", xintercept = 0, 
                 size = 0.6, color = "grey40") +
      ggdist::stat_pointinterval() +
      theme_scoringutils() +
      labs(y = "", x = "Differences in ranking")

@@

# should probably have one plot for both cases and deaths since this is rankings
p_diff_cases <- plot_ranking_diffs(rankings, rankings_diff, 
                                   target_type = "Cases")

ggsave(filename = "output/figures/HUB-ranking-diffs.png", 
       plot = p_diff_cases,
       width = 9, height = 5)

rankings_diff |>
  group_by(horizon, target_type) |>
  summarise(cor = cor(natural, log))
```

@@

```{r}
summarised_pairwise <- scores |>
  filter(horizon == 2, 
         target_type == "Cases") |>
  summarise_scores(by = c("model", "scale"), relative_skill = TRUE)

@@

#Issues: this currently ignores that some models have only made forecasts for one location. They should usually be excluded, but maybe not necessary here as we're really more comparing the results for natural and log rather than the models against each other.

cor(diffs$log, diffs$natural)

# "CovidMetrics-epiBATS" only has forecasts in DE
# "ICM-agentModel" only in Poland
# "UVA is everywhere
hub_data |>
  filter(model == "UVA-Ensemble") |> check_forecasts()

@@

ggsave(filename = "output/figures/HUB-model-ICM.png", width = 7, height = 4.5, plot = ICM)
ggsave(filename = "output/figures/HUB-model-epiBATS.png", width = 7, height = 4.5, plot = epiBATS)
ggsave(filename = "output/figures/HUB-model-BSLCoV.png", width = 7, height = 4.5, plot = BSLCoV)

@@

## Variance of scores across locations

>>>>

```{r}
# average number of cases and deaths

@@

ggsave("output/figures/HUB-mean-obs-location.png", width = 9, height = 7)

@@

```{r}
rankings <- scores |>
  select(-c(coverage_deviation, bias, ae_median, dispersion, underprediction, overprediction)) |>
  group_by(location, forecast_date, horizon, target_type, scale) |>
  mutate(ranking = rank(interval_score) / n()) |>
  ungroup()

rankings_wide <- rankings |>
  select(model, location, target_end_date, forecast_date, horizon,
         interval_score, scale, ranking, target_type) |>
  pivot_wider(names_from = scale, values_from = ranking, 
              id_cols = -interval_score)

plot_ranking_diffs <- function(
  rankings, 
  rankings_wide,
  target_type
) {
  type <- target_type
  # maybe replace this by the same ranking for all plots
  factor_levels <- rankings |>
    filter(horizon == 2, scale == "natural", target_type == type) |>
    group_by(model) |>
    summarise(ranking = mean(ranking)) |>
    arrange(-ranking) |>
    pull(model)

@@

  ranking_plot <- function(
    hor
  ) {
    p <- rankings_wide |>
      mutate(diff_ranking = natural - log) |>
      mutate(model = factor(model, levels = factor_levels)) |>
      filter(horizon == hor, 
             !is.na(model)) |>
      ggplot(aes(y = model, x = diff_ranking)) +
      geom_vline(linetype = "dashed", xintercept = 0, 
                 size = 0.6, color = "grey40") +
      ggdist::stat_pointinterval() +
      theme_scoringutils() +
      labs(y = "", x = "Differences in ranking")

@@

# should probably have one plot for both cases and deaths since this is rankings
p_diff_cases <- plot_ranking_diffs(rankings, rankings_wide, 
                                   target_type = "Cases")

ggsave(filename = "output/figures/HUB-ranking-diffs.png", 
       plot = p_diff_cases,
       width = 9, height = 5)
```

@@

```{r}
summarised_pairwise <- scores |>
  filter(target_type == "Cases") |>
  summarise_scores(by = c("model", "scale"), relative_skill = TRUE)

@@

#Issues: this currently ignores that some models have only made forecasts for one location. They should usually be excluded, but maybe not necessary here as we're really more comparing the results for natural and log rather than the models against each other.
```

# Correlations for ranks, scores and pairwise comparisons

```{r}
# correlation between values
hub_data |>
  select(location, target_end_date, target_type, true_value) |>
  unique() |>
  mutate(log_obs = log(pmax(true_value, 0) + 1)) |>
  group_by(target_type) |>
  summarise(cor = cor(true_value, log_obs))

# correlation between scores
cor_scores <- scores |>
  filter(horizon <=4) |>
  select(interval_score, scale, forecast_date, model, horizon, location, target_type) |>
  pivot_wider(names_from = scale, values_from = interval_score) |>
  group_by(horizon, target_type) |>
  summarise(cor = cor(natural, log), 
            spearman = cor(natural, log))

cor_scores |> 
  mutate(`Target type` = target_type) |>
  ggplot(aes(x = horizon, y = cor, 
             fill = `Target type`, color = `Target type`)) + 
  geom_histogram(stat = "identity", position = "dodge") +
  theme_scoringutils() + 
  coord_cartesian(ylim = c(0, 1)) +
  labs(y = "Correlation (scores natural vs. log)", x = "Forecast horizon")

# Correlation between ranks when going from natural to log
correlation_ranks <- rankings_wide |>
  filter(horizon < 5) |>
  group_by(horizon, target_type) |>
  summarise(cor = cor(natural, log)) |>
  rename(`Target type` = target_type)

plot_cor_ranks <- correlation_ranks |>
  ggplot(aes(x = horizon, y = cor, 
             fill = `Target type`, color = `Target type`)) + 
  geom_histogram(stat = "identity", position = "dodge") +
  theme_scoringutils() + 
  coord_cartesian(ylim = c(0, 1)) +
  labs(y = "Correlation (rank natural vs. log)", x = "Forecast horizon")

ggsave(filename = "output/figures/HUB-cor-ranks.png", width = 7, height = 4.5, 
       plot = plot_cor_ranks)

# Correlation between pairwise comparisons
correlation_rel_skill <- scores |>
  filter(horizon < 5) |>
  summarise_scores(
    by = c("model", "scale", "horizon", "target_type"), 
    relative_skill = TRUE) |>
  select(model, horizon, target_type, relative_skill, scale) |>
  pivot_wider(values_from = relative_skill, names_from = scale) |>
  group_by(horizon, target_type) |>
  summarise(cor = cor(natural, log))

plot_cor_skill <- correlation_rel_skill |>
  rename(`Target type` = target_type) |>
  ggplot(aes(x = horizon, y = cor, fill = `Target type`, color = `Target type` )) + 
  # geom_line() +
  # geom_point() +
  geom_histogram(stat = "identity", position = "dodge") +
  theme_scoringutils() + 
  coord_cartesian(ylim = c(0, 1)) +
  labs(y = "Correlation (rel. skill natural vs. log)", x = "Forecast horizon")

ggsave(filename = "output/figures/HUB-cor-rel-skill.png", width = 7, height = 4.5, 
       plot = plot_cor_skill)

plot_cors <- plot_cor_ranks + plot_cor_skill +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

ggsave(filename = "output/figures/HUB-cors-skill-rank.png", width = 7, height = 3, 
       plot = plot_cors)

Example comparisons of forecasts on the log and the natural scale

```{r}
# "CovidMetrics-epiBATS" only has forecasts in DE
# "ICM-agentModel" only in Poland
# "UVA is everywhere

@@

ggsave(filename = "output/figures/HUB-model-ICM.png", width = 9, height = 5, plot = ICM)
ggsave(filename = "output/figures/HUB-model-epiBATS.png", width = 9, height = 5, plot = epiBATS)
ggsave(filename = "output/figures/HUB-model-BSLCoV.png", width = 9, height = 5, plot = BSLCoV)

# Table with relevant values

```{r}
summary <- hub_data |>
  filter(horizon == 2) |>
  mutate(natural = true_value, 
         log = log(pmax(0, true_value) +1)) |>
  select(location, target_type, target_end_date, natural, log) |>
  pivot_longer(cols = c(natural, log), values_to = "true_value", names_to = "scale") |>
  unique() |>
  group_by(target_type, scale) |>
  summarise(mean = mean(true_value), 
            sd = sd(true_value), 
            var = var(true_value))

table_obs <- summary |>
  pivot_longer(cols = c(mean, sd, var), names_to = "measure") |>
  pivot_wider(values_from = value, names_from = scale) |>
  select(target_type, measure, natural, log) |>
  mutate(quantity = "Observations", 
         natural = round(natural), 
         log = round(log, 2)) |>
  select(target_type, quantity, measure, natural, log)

table_scores <- scores |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, scale) |>
  summarise(mean = mean(interval_score), 
            sd = sd(interval_score), 
            .groups = "drop_last") |>
  pivot_longer(cols = c(mean, sd), names_to = "measure") |>
  pivot_wider(values_from = value, names_from = scale) |>
 mutate(quantity = "WIS", 
         natural = round(natural), 
         log = round(log, 2)) |>
  select(target_type, quantity, measure, natural, log)

table <- rbind(table_obs, 
               table_scores) |>
  arrange(quantity, target_type, measure)

table |>
  kable(format = "latex", booktabs = TRUE,
        align = c("l", "l", "l", rep("c", 2)),
        # col.names = c(" ", names(scores)[-(1:2)])) %>%
  ) #|>
  # collapse_rows(columns = 1) %>%
  # kable_styling(latex_options = c("scale_down",
  #                                 "hold_position")) %>%
  # column_spec(1, background = "white") %>%
  # pack_rows("Observations", 1, 6, indent = FALSE,
  #           hline_after = TRUE) %>%
  # pack_rows("WIS", 7, 10, indent = FALSE,
  #           hline_after = TRUE)

@@

## Variance of scores vs. mean of scores across locations

### 2022-07-21 main.tex
update manuscript

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} and the Weighted Interval Score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and represent a generalisation of the absolute error to full predictive distributions (see details in the SI). The WIS can be thought of as an approxmiation of the CRPS for forecasts in a quantile format and has very similar properties (the WIS converges towards the CRPS for an increasing set of equally-spaced prediction intervals). Due to its widespread use in epidemiology (and its similarity to the CRPS) we focus on the WIS in this paper, ignoring other proper scoring rules.

@@

Now consider a forecast on $\log y_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon_{t+1} \Leftrightarrow \\
\varepsilon'_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (\frac{y_{t+1}}{y_t}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between} \hat{g}_{t, t+1} and g_{t, t+1}. 
\end{align}

This approximation breaks down when the difference between the predicted and the actual growth rate becomes too large (albeit forecasts are still evaluated in terms of relative errors). If this is of great concern one may want to use a different transformation like dividing forecasts and observations by the last known values instead in order to score the growth rate explicitly.

@@

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, aggregate scores across multiple forecasts are affected by the fact some scores will in general be much larger than others. On the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values. Even an ideal forecaster will make much larger errors when predicting a quantity such as reported case numbers, than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values. 
Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest. 
For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

If one finds that average scores are dominated by forecasts for small quantities one could omit these forecasts entirely, arguing that relative errors are difficult to meaningfully interpret for small quantities. One might also take a more experimental route, namely adding a number $n$ (e.g. $n = 100$) to all observations and forecasts before taking the logarithm. This also constitutes a strictly monotonic transformation which preserves propriety and would reduce all scores (through reducing relative errors). Scores for forecasts on small quantities would be particularly affected, resulting in a more equal distribution of scores for forecasts of differing orders of magntitudes. Researchers could choose to add either a small or large number, depending on how much they want to equalise relative errors when aggregating scores. 
I KNOW YOU ALL HATE THIS, BUT IT IS SOOOO CLEVER! :-(

@@

PUT SOMEWHERE ELSE
Conveniently, the decomposition of the WIS into dispersion, overprediction and underprediction is preserved. The interpretation of the components has now changed in that they now (approximately) represent uncertainty, over-prediction, and under-prediction with the growth rate and so are independent of current incidence.

@@

\paragraph{Introduction to the Forecast Hub} As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries.

\paragraph{Describing features of the data}
Across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with an overall standard deviation of 47135 (831). The number of observed value does not only differ by forecast target, but also shows considerable heterogeneity by location (see Figure \ref{fig:HUB-mean-locations}. Across the different locations, the variance in observed values is roughly equal to the square of the mean, suggesting that, for a given location, both cases and deaths are not poisson-distributed, but rather exhibit over-dispersion. 
% MAYBE FIT A NEGATIVE BINOMIAL TO THESE OBSERVATIONS

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{CAPTION}
    \label{fig:HUB-mean-locations}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-var-obs.png}
    \caption{Observed mean against observed variance of observations. The dashed line marks what would be expecetd from a negative binomially distributed variable with variance of the observed value equal to the mean + the square of mean observed value. }
    \label{fig:HUB-variance-mean}
\end{figure}

\paragraph{Features of the scores}
Across all time points and locations, the mean number weighted interval score on the natural scale for cases (deaths) was 8855 (59.3) with an overall standard deviation of 51274 (156). On the log scale, scores were much closer to each other (see Figure \ref{fig:HUB-average-scores}), with a mean WIS for cases (deaths) of 0.507 (0.362) with an overall standard deviation of 0.745 (0.407). 
% NEED A TABLE WITH SCORES for the Appendix
On the natural scale, scores vary by several orders of magnitudes across locations (see \ref{fig:HUB-scores-location}), whereas variation across locations is much smaller for scores on the log scale and wis values are more evenly distributed. The ordering of scores across locations is not preserved when going from the natural to the log scale (see Figure \ref{fig:HUB-mean-location}. Rather, there seems to be a slight inverse relationship that locations which previously had low scores now tend to receive higher scores. 
The correlation between scores on the log and natural scale for different locations is XX for cases and XX for deaths. 
BUT: CORRELATION FOR RANKINGS IS STILL LAGRGE

@@

\paragraph{Rankings}
Rankings do change a little bit, but not massively. More difference comes when we look at greater forecast horizons.
Really this is more a point about how rankings change even for one single forecast (which I originally thought they shouldn't). Would be good to tease out what happens here. Somewhow we do change our judegement on which model is better. Maybe the preservation of the order really only holds for one interval? Or maybe not even that? 
Example: True value = 1
Forecaster 1: 0.8, 3.     Natural scale: 3.2 - 0.8 = 2.4.     Log scale: log 3 - log 0.8 = 1.386
Forecaster 2: 0.5, 2.8    Natural scale: 2.8 - 0.5 = 2.3    Log scale: log (2.8/0.5) = 1.722767
So one effect is that for a given dispersion on the natural scale, it's better if that interval is skewed, as that implies that at least you only off a lot in one direction in negative terms, and not in the other direction. Maybe looking at over-and underprediction is the key here. 
%ADD SAME PLOT TO SI FOR HORIZON 4.

@@

>>>>

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} and the Weighted Interval Score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and represent a generalisation of the absolute error to full predictive distributions (see details in the SI). The WIS can be thought of as an approxmiation of the CRPS for forecasts in a quantile format and has very similar properties (the WIS converges towards the CRPS for an increasing set of equally-spaced prediction intervals). Due to its widespread use in epidemiology (and its similarity to the CRPS) we mostly focus on the WIS in this paper, ignoring other proper scoring rules. Formulas for the WIS are given in the SI.

@@

Now consider a forecast on $\log y_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon_{t+1} \Leftrightarrow \\
\varepsilon'_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (\frac{y_{t+1}}{y_t}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1}) \Leftrightarrow \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between } \hat{g}_{t, t+1} \text{ and } g_{t, t+1}. 
\end{align}

This approximation breaks down when the difference between the predicted and the actual growth rate becomes too large (albeit forecasts are still evaluated in terms of relative errors). If this is of great concern one may want to use a different transformation like dividing forecasts and observations by the last known values instead in order to score the growth rate explicitly (although this lacks the elegance of having one single transformation per time point).

Conveniently, the decomposition of the WIS into dispersion, overprediction and underprediction is preserved. The interpretation of the components has now changed in that they now (approximately) represent uncertainty, over-prediction, and under-prediction with the growth rate and so are independent of current incidence.

@@

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, aggregate scores across multiple forecasts are affected by the fact some scores will in general be much larger than others. On the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values. Even an ideal forecaster will make much larger errors when predicting a quantity such as reported case numbers, than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values. 
Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest.

MAYBE MOVE TO SI
For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

I KNOW YOU ALL ARE GOING TO HATE THIS, BUT IT IS SOOOO CLEVER! :-(
If one finds that average scores are dominated by forecasts for small quantities one could omit these forecasts entirely, arguing that relative errors are difficult to meaningfully interpret for small quantities. One might also take a more experimental route, namely adding a number $n$ (e.g. $n = 100$) to all observations and forecasts before taking the logarithm. This also constitutes a strictly monotonic transformation which preserves propriety and would reduce all scores (through reducing relative errors). Scores for forecasts on small quantities would be particularly affected, resulting in a more equal distribution of scores for forecasts of differing orders of magntitudes. Researchers could choose to add either a small or large number, depending on how much they want to equalise relative errors when aggregating scores.

@@

@@

As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries. Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

Pooled across all time points and locations, the mean number of cases (deaths) observed was 22811 (368) with an overall standard deviation of 47135 (831) (see Table \ref{tab:HUB-summary}). The average number of observed cases and deaths varies considerably by location (see Figure \ref{fig:HUB-mean-locations}A and B). Observations are overdispersed, meaning that for a given location, the variance in observations exceeds the mean of all observed values (see Figure \ref{fig:HUB-variance-mean}). 
%maybe make a line of best fit of the form variance = alpha * mean^2 + beta * mean

Pooled across all time points and locations, the mean WIS on the natural scale for cases (deaths) was 8855 (59.3) with an overall standard deviation of 51274 (156) (see Table \ref{tab:HUB-summary}). On the log scale, scores were much closer to each other (see Figure \ref{fig:HUB-average-scores}), with a mean WIS for cases (deaths) of 0.507 (0.362) with an overall standard deviation of 0.745 (0.407).

Variation of scores across targets (see Figure XX) and locations (see Figure \ref{fig:HUB-mean-locations}A, B) is much larger on the natural than on the log scale, where scores are more evenly distributed. On the natural scale, average scores per location correlate strongly (XX) with the average number of observed cases or deaths (See Figure XX). On the log scale, this correlation is much weaker and slightly negative. Forecasts across different locations receive more similar scores, with a tendency for scores to be slightly higher in locations with few observed cases and deaths (see Figures XX and \ref{fig:HUB-mean-locations}. 
%This is in line with the observation that the association between variance is smaller than mu^2 + mu, meaning that we would expect this. 
For individual forecasts, rankings between models are mostly preserved (correlation: X for cases, Y for deaths), with differences increasing across forecast horizons (see Figure \ref{fig:HUB-cors-scores}).

The correlation between scores on the log and natural scale for different locations is XX for cases and XX for deaths. 
The correlation between the actual observations is 0.628 for cases and 0.631 for deaths. IS THAT HELPFUL?

\begin{table}[h!]]
    \centering

    \begin{tabular}{lllcc}
    \toprule
    target\_type & quantity & measure & natural & log\\
    \midrule
    Cases & Observations & mean & 20308 & 8.39\\
    Cases & Observations & sd & 43405 & 2.11\\
    Cases & Observations & var & 1884002308 & 4.46\\
    Deaths & Observations & mean & 259 & 3.79\\
    Deaths & Observations & sd & 532 & 2.11\\
    \addlinespace
    Deaths & Observations & var & 283492 & 4.46\\
    Cases & WIS & mean & 4544 & 0.28\\
    Cases & WIS & sd & 17585 & 0.49\\
    Deaths & WIS & mean & 28 & 0.22\\
    Deaths & WIS & sd & 67 & 0.26\\
    \bottomrule
    \end{tabular}

    \caption{CAPTION}
    \label{tab:HUB-summary}
\end{table}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{Scores and average observed values across 1ocations. A, B: Mean of observed cases and deaths across all time points for different locations. C, D: XXX WIS for forecasts made by the Hub ensemble. D, E: Average WIS for log-transformed forecasts. }
    \label{fig:HUB-mean-locations}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-var-obs.png}
    \caption{Observed mean against observed variance of observations in different locations across time. The dashed line marks what would be expecetd from a negative binomially distributed variable with variance of the observed value equal to the mean + the square of mean observed value. }
    \label{fig:HUB-variance-mean}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-cors-skill-rank.png}
    \caption{Correlation between scores on the natural and on the log scale. A: Correlation between relative ranks (the rank in terms of WIS divided by the number of models) for individual forecasts, separated by forecast horizon. B: Correlation between relative skill values achieved by models across locations and time points, separated by forecast horizon.}
    \label{fig:HUB-cors-scores}
\end{figure}

@@

\paragraph{Rankings}
So one effect is that for a given dispersion on the natural scale, it's better if that interval is skewed, as that implies that at least you only off a lot in one direction in negative terms, and not in the other direction. Maybe looking at over-and underprediction is the key here. 
%ADD SAME PLOT TO SI FOR HORIZON 4.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-model-ICM.png}
    \caption{Top: 2-week-ahead predictions. Bottom: scores }
    \label{fig:HUB-model-ICM}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-model-epiBATS.png}
    \caption{Top: 2-week-ahead predictions. Bottom: scores }
    \label{fig:HUB-model-epiBATS}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-model-BSLCoV.png}
    \caption{Top: 2-week-ahead predictions. Bottom: scores }
    \label{fig:HUB-model-BSLCoV}
\end{figure}
